---
title: "Corona on the continents"
author: "Pieter Hobbelen"
date: "6/21/2020"
output: html_document
---

```{r load the libraries, echo=FALSE, message=FALSE}
library(tidyverse)
library(ggrepel)
library(knitr)
library(kableExtra)
```

```{r load the datasets, echo=FALSE, message=FALSE}
Mexico_pop <- 128932753
USA_pop <- 331002651
Canada_pop <- 37742154
Cuba_pop <- 11326616
Domenican_Republic_pop <- 10847910
Guatemala_pop <- 17915568
Belize_pop <- 397628
Honduras_pop <- 9904607
El_Salvador_pop <- 6486205
Nicaragua_pop <- 6624554
Costa_Rica_pop <- 5094118
Panama_pop <- 4314767
Brazil_pop <- 212559417
Peru_pop <- 32971854
Argentinia_pop <- 45195774
Venezuala_pop <- 28435940
Surinama_pop <- 586632
South_Africa_Country_pop <- 59308690
Madagascar_pop <- 27691018
Tanzania_pop <- 59734218
Zambia_pop <- 18383955
Cameroon_pop <- 26545863
Egypt_pop <- 102334404
Ethiopia_pop <- 114963588
Uganda_pop <- 45741007
Eritrea_pop <- 3546421
Morocco_pop <- 36910560
Libya_pop <- 6871292
Mali_pop <- 20250833
Ghana_pop <- 31072940
Nigeria_pop <- 206139589
Chad_pop <- 16425864
Spain_pop <- 46754778
UK_pop <- 67886011
Sweden_pop <- 10099265
Germany_pop <- 83783942
Italy_pop <- 60461826
Iceland_pop <- 341243
Latvia_pop <- 1886198
Greece_pop <- 10423054
Russia_pop <- 145934462
Serbia_pop <- 8737371
Croatia_pop <- 4105267
Ukraine_pop <- 43733762
Slovakia_pop <- 5459642
Yemen_pop <- 29825964
Saudi_Arabia_pop <- 34813871
Iran_pop <- 83992949
Pakistan_pop <- 220892340
India_pop <- 1380004385
Indonesia_pop <- 273523615
Thailand_pop <- 69799978
Philippines_pop <- 109581078
Myanmar_pop <- 54409800
China_pop <- 1439323776
South_Korea_pop <- 51269185
Japan_pop <- 126476461
Mongolia_pop <- 3278290
Australia_pop <- 25499884
New_Zealand_pop <- 4882233
Papoea_New_Guinea_pop <- 8947024
Falklandislands_pop <- 3480
Fiji_pop <- 896445
Antigua_and_Barbuda_pop <- 97929
British_Virgin_Island_pop <- 30231
Greenland_pop <- 56770
New_Caledonia_pop <- 285498
Bermuda_pop <- 62278
Faeroer_pop <- 48863



Mexico_conf_cases <- 165000
USA_conf_cases <- 2230000
Canada_conf_cases <- 100000
Cuba_conf_cases <- 2295
Domenican_Republic_conf_cases <- 24645
Guatemala_conf_cases <- 11868
Belize_conf_cases <- 22
Honduras_conf_cases <- 10739
El_Salvador_conf_cases <- 4329
Nicaragua_conf_cases <- 1823
Costa_Rica_conf_cases <- 1939
Panama_conf_cases <- 23351
Brazil_conf_cases <- 984000
Peru_conf_cases <- 244000
Argentinia_conf_cases <- 37497
Venezuala_conf_cases <- 3386
Surinama_conf_cases <- 277
South_Africa_Country_conf_cases <- 83890
Madagascar_conf_cases <- 1403
Tanzania_conf_cases <- 509
Zambia_conf_cases <- 1416
Cameroon_conf_cases <- 10638
Egypt_conf_cases <- 50437
Ethiopia_conf_cases <- 3954
Uganda_conf_cases <- 741
Eritrea_conf_cases <- 142
Morocco_conf_cases <- 9042
Libya_conf_cases <- 510
Mali_conf_cases <- 1906
Ghana_conf_cases <- 12929
Nigeria_conf_cases <- 18480
Chad_conf_cases <- 854
Spain_conf_cases <- 245000
UK_conf_cases <- 300000
Sweden_conf_cases <- 56043 
Germany_conf_cases <- 190000
Italy_conf_cases <- 238000
Iceland_conf_cases <- 1816
Latvia_conf_cases <- 1108
Greece_conf_cases <- 3227
Russia_conf_cases <- 568000
Serbia_conf_cases <- 12616
Croatia_conf_cases <- 2269
Ukraine_conf_cases <- 34984
Slovakia_conf_cases <- 1562
Yemen_conf_cases <- 909
Saudi_Arabia_conf_cases <- 146000
Iran_conf_cases <- 198000
Pakistan_conf_cases <- 165000
India_conf_cases <- 381000
Indonesia_conf_cases <- 43803
Thailand_conf_cases <- 3146
Philippines_conf_cases <- 28459
Myanmar_conf_cases <- 286
China_conf_cases <- 83325
South_Korea_conf_cases <- 12306 
Japan_conf_cases <- 17740
Mongolia_conf_cases <- 204
Australia_conf_cases <- 7409
New_Zealand_conf_cases <- 1157
Papoea_New_Guinea_conf_cases <- 8
Falklandislands_conf_cases <- 13
Fiji_conf_cases <- 18
Antigua_and_Barbuda_conf_cases <- 26
British_Virgin_Island_conf_cases <- 8
Greenland_conf_cases <- 13
New_Caledonia_conf_cases <- 21
Bermuda_conf_cases <- 144
Faeroer_conf_cases <- 187

  
Mexico_death_cases <- 19747
USA_death_cases <- 120000
Canada_death_cases <- 8300
Cuba_death_cases <- 85
Domenican_Republic_death_cases <- 635
Guatemala_death_cases <- 449
Belize_death_cases <- 2
Honduras_death_cases <- 343
El_Salvador_death_cases <- 86
Nicaragua_death_cases <- 64
Costa_Rica_death_cases <- 12
Panama_death_cases <- 475
Brazil_death_cases <- 47897
Peru_death_cases <- 7461
Argentinia_death_cases <- 948
Venezuala_death_cases <- 28
Surinama_death_cases <- 8
South_Africa_Country_death_cases <- 1737
Madagascar_death_cases <- 13 
Tanzania_death_cases <- 21
Zambia_death_cases <- 11
Cameroon_death_cases <- 282
Egypt_death_cases <- 1938
Ethiopia_death_cases <- 65
Uganda_death_cases <-  0
Eritrea_death_cases <- 0
Morocco_death_cases <- 213
Libya_death_cases <- 10
Mali_death_cases <- 107
Ghana_death_cases <- 66
Nigeria_death_cases <- 475
Chad_death_cases <- 74
Spain_death_cases <- 28313
UK_death_cases <- 42288
Sweden_death_cases <- 5053
Germany_death_cases <- 8946
Italy_death_cases <- 34514
Iceland_death_cases <- 10
Latvia_death_cases <- 30
Greece_death_cases <- 188
Russia_death_cases <- 7841
Serbia_death_cases <- 258
Croatia_death_cases <- 107
Ukraine_death_cases <- 985
Slovakia_death_cases <- 28
Yemen_death_cases <- 248
Saudi_Arabia_death_cases <- 1139
Iran_death_cases <- 9392
Pakistan_death_cases <- 3229
India_death_cases <- 12573
Indonesia_death_cases <- 2373
Thailand_death_cases <- 58
Philippines_death_cases <- 1130
Myanmar_death_cases <- 6
China_death_cases <- 4634
South_Korea_death_cases <- 280
Japan_death_cases <- 935
Mongolia_death_cases <- 0
Australia_death_cases <- 102
New_Zealand_death_cases <- 22
Papoea_New_Guinea_death_cases <- 0
Falklandislands_death_cases <- 0
Fiji_death_cases <- 0
Antigua_and_Barbuda_death_cases <- 3
British_Virgin_Island_death_cases <- 1
Greenland_death_cases <- 0
New_Caledonia_death_cases <- 0
Bermuda_death_cases <- 9
Faeroer_death_cases <- 0


North_America_pop <- Mexico_pop + USA_pop + Canada_pop
Mid_America_pop <- Cuba_pop + Domenican_Republic_pop + Guatemala_pop + Belize_pop + Honduras_pop + El_Salvador_pop + Nicaragua_pop + Costa_Rica_pop + Panama_pop
South_America_pop <- Brazil_pop + Peru_pop + Argentinia_pop + Venezuala_pop + Surinama_pop
South_Africa_pop <- South_Africa_Country_pop + Madagascar_pop + Tanzania_pop + Zambia_pop
Mid_East_Africa_pop <- Cameroon_pop + Egypt_pop + Ethiopia_pop + Uganda_pop + Eritrea_pop
North_West_Africa_pop <- Morocco_pop + Libya_pop + Mali_pop + Ghana_pop + Nigeria_pop + Chad_pop
North_West_Europe_pop <- Spain_pop + UK_pop + Sweden_pop + Germany_pop + Italy_pop + Iceland_pop + Latvia_pop
East_Europe_pop <- Greece_pop + Russia_pop + Serbia_pop + Croatia_pop + Ukraine_pop + Slovakia_pop
South_West_Azia_pop <- Yemen_pop + Saudi_Arabia_pop + Iran_pop + Pakistan_pop
South_East_Azia_pop <- India_pop + Indonesia_pop + Thailand_pop + Philippines_pop + Myanmar_pop
Mid_Azia_pop <- China_pop + South_Korea_pop + Japan_pop + Mongolia_pop
Oceania_pop <- Australia_pop + New_Zealand_pop + Papoea_New_Guinea_pop
Pacific_and_Atlantic_Island_pop <- Falklandislands_pop + Fiji_pop + Antigua_and_Barbuda_pop + British_Virgin_Island_pop + Greenland_pop + New_Caledonia_pop + 
  Bermuda_pop + Faeroer_pop
  

North_America_conf_cases <- Mexico_conf_cases + USA_conf_cases + Canada_conf_cases
Mid_America_conf_cases <- Cuba_conf_cases + Domenican_Republic_conf_cases + Guatemala_conf_cases + Belize_conf_cases + Honduras_conf_cases + El_Salvador_conf_cases + 
  Nicaragua_conf_cases + Costa_Rica_conf_cases + Panama_conf_cases
South_America_conf_cases <- Brazil_conf_cases + Peru_conf_cases + Argentinia_conf_cases + Venezuala_conf_cases + Surinama_conf_cases
South_Africa_conf_cases <- South_Africa_Country_conf_cases + Madagascar_conf_cases + Tanzania_conf_cases + Zambia_conf_cases
Mid_East_Africa_conf_cases <- Cameroon_conf_cases + Egypt_conf_cases + Ethiopia_conf_cases + Uganda_conf_cases + Eritrea_conf_cases
North_West_Africa_conf_cases <- Morocco_conf_cases + Libya_conf_cases + Mali_conf_cases + Ghana_conf_cases + Nigeria_conf_cases + Chad_conf_cases
North_West_Europe_conf_cases <- Spain_conf_cases + UK_conf_cases + Sweden_conf_cases + Germany_conf_cases + Italy_conf_cases + Iceland_conf_cases + Latvia_conf_cases
East_Europe_conf_cases <- Greece_conf_cases + Russia_conf_cases + Serbia_conf_cases + Croatia_conf_cases + Ukraine_conf_cases + Slovakia_conf_cases
South_West_Azia_conf_cases <- Yemen_conf_cases + Saudi_Arabia_conf_cases + Iran_conf_cases + Pakistan_conf_cases
South_East_Azia_conf_cases <- India_conf_cases + Indonesia_conf_cases + Thailand_conf_cases + Philippines_conf_cases + Myanmar_conf_cases
Mid_Azia_conf_cases <- China_conf_cases + South_Korea_conf_cases + Japan_conf_cases + Mongolia_conf_cases
Oceania_conf_cases <- Australia_conf_cases + New_Zealand_conf_cases + Papoea_New_Guinea_conf_cases
Pacific_and_Atlantic_Island_conf_cases <- Falklandislands_conf_cases + Fiji_conf_cases + Antigua_and_Barbuda_conf_cases + British_Virgin_Island_conf_cases + 
  Greenland_conf_cases + New_Caledonia_conf_cases + Bermuda_conf_cases + Faeroer_conf_cases

North_America_death_cases <- Mexico_death_cases + USA_death_cases + Canada_death_cases
Mid_America_death_cases <- Cuba_death_cases + Domenican_Republic_death_cases + Guatemala_death_cases + Belize_death_cases + Honduras_death_cases + El_Salvador_death_cases + 
  Nicaragua_death_cases + Costa_Rica_death_cases + Panama_death_cases
South_America_death_cases <- Brazil_death_cases + Peru_death_cases + Argentinia_death_cases + Venezuala_death_cases + Surinama_death_cases
South_Africa_death_cases <- South_Africa_Country_death_cases + Madagascar_death_cases + Tanzania_death_cases + Zambia_death_cases
Mid_East_Africa_death_cases <- Cameroon_death_cases + Egypt_death_cases + Ethiopia_death_cases + Uganda_death_cases + Eritrea_death_cases
North_West_Africa_death_cases <- Morocco_death_cases + Libya_death_cases + Mali_death_cases + Ghana_death_cases + Nigeria_death_cases + Chad_death_cases
North_West_Europe_death_cases <- Spain_death_cases + UK_death_cases + Sweden_death_cases + Germany_death_cases + Italy_death_cases + Iceland_death_cases + Latvia_death_cases
East_Europe_death_cases <- Greece_death_cases + Russia_death_cases + Serbia_death_cases + Croatia_death_cases + Ukraine_death_cases + Slovakia_death_cases
South_West_Azia_death_cases <- Yemen_death_cases + Saudi_Arabia_death_cases + Iran_death_cases + Pakistan_death_cases
South_East_Azia_death_cases <- India_death_cases + Indonesia_death_cases + Thailand_death_cases + Philippines_death_cases + Myanmar_death_cases
Mid_Azia_death_cases <- China_death_cases + South_Korea_death_cases + Japan_death_cases + Mongolia_death_cases
Oceania_death_cases <- Australia_death_cases + New_Zealand_death_cases + Papoea_New_Guinea_death_cases
Pacific_and_Atlantic_Island_death_cases <- Falklandislands_death_cases + Fiji_death_cases + Antigua_and_Barbuda_death_cases + British_Virgin_Island_death_cases + 
  Greenland_death_cases + New_Caledonia_death_cases + Bermuda_death_cases + Faeroer_death_cases


Region <- c("North America", "Mid America", "South America", "South Africa", "Mid East Africa", "North West Africa", "North West Europe", "East Europe", 
                        "South West Azia", "South East Azia","Mid Azia", "Oceania", "Pacific and Atlantic Islands")

Abb_region <- c("N America", "Mid America", "S America", "S Africa", "ME Africa", "NW Africa", "NW Europe", "E Europe", 
            "SW Azia", "SE Azia","M Azia", "Oceania", "Pac. Atl. Islands")

Continent <- c("North America", "North America", "South America", "Africa", "Africa", "Africa", "Europe", "Europe", "Azia", "Azia","Azia", "Oceania", 
                        "Other")

Reliability_test_capacity <- c("Good", "Bad", "Bad", "Bad", "Bad", "Bad", "Very Good", "Good", 
            "Bad", "Bad","Normal", "Good", "Bad")


western_countries <- c("Spain", "UK", "Sweden", "Germany", "Italy", "Iceland", "Latvia", "Greece", "Russia", "Serbia", "Croatia", "Ukraine", "Slovakia", "USA", "Canada", 
                       "Australia", "New Zealand")

news_states_western_countries <- c("Problem", "Problem", "Normal Corona rate", "Normal Corona rate", "Problem", "Normal Corona rate", "Low Corona rate", "Low Corona rate", "Normal Corona rate", "Low Corona rate", "Low Corona rate", "Low Corona rate", "Low Corona rate", "Problem", "High Corona rate", "Low Corona rate", "Low Corona rate")

western_countries_pop <- c(Spain_pop, UK_pop, Sweden_pop, Germany_pop, Italy_pop, Iceland_pop, Latvia_pop, Greece_pop, Russia_pop, Serbia_pop, Croatia_pop, Ukraine_pop, 
                           Slovakia_pop, USA_pop, Canada_pop, Australia_pop, New_Zealand_pop)

western_countries_confirmed <- c(Spain_conf_cases, UK_conf_cases, Sweden_conf_cases, Germany_conf_cases, Italy_conf_cases, Iceland_conf_cases, Latvia_conf_cases, Greece_conf_cases,
                                 Russia_conf_cases, Serbia_conf_cases, Croatia_conf_cases, Ukraine_conf_cases, Slovakia_conf_cases, USA_conf_cases, Canada_conf_cases, 
                                 Australia_conf_cases, New_Zealand_conf_cases)

western_countries_deaths <- c(Spain_death_cases, UK_death_cases, Sweden_death_cases, Germany_death_cases, Italy_death_cases, Iceland_death_cases, Latvia_death_cases, Greece_death_cases,
                              Russia_death_cases, Serbia_death_cases, Croatia_death_cases, Ukraine_death_cases, Slovakia_death_cases, USA_death_cases, Canada_death_cases, 
                              Australia_death_cases, New_Zealand_conf_cases)

western_countries_confirmed_rate <- western_countries_confirmed/western_countries_pop
western_countries_deaths_rate <- western_countries_deaths/western_countries_pop 

Population <- c(North_America_pop, Mid_America_pop, South_America_pop, South_Africa_pop, Mid_East_Africa_pop, North_West_Africa_pop, North_West_Europe_pop, 
                                   East_Europe_pop, South_West_Azia_pop, South_East_Azia_pop, Mid_Azia_pop, Oceania_pop, Pacific_and_Atlantic_Island_pop)

Confirmed_cases <- c(North_America_conf_cases, Mid_America_conf_cases, South_America_conf_cases, South_Africa_conf_cases, Mid_East_Africa_conf_cases, 
                           North_West_Africa_conf_cases, North_West_Europe_conf_cases, East_Europe_conf_cases, South_West_Azia_conf_cases, South_East_Azia_conf_cases,
                           Mid_Azia_conf_cases, Oceania_conf_cases, Pacific_and_Atlantic_Island_conf_cases)

Death_cases <- c(North_America_death_cases, Mid_America_death_cases, South_America_death_cases, South_Africa_death_cases, Mid_East_Africa_death_cases, 
                 North_West_Africa_death_cases, North_West_Europe_death_cases, East_Europe_death_cases, South_West_Azia_death_cases, South_East_Azia_death_cases,
                 Mid_Azia_death_cases, Oceania_death_cases, Pacific_and_Atlantic_Island_death_cases)

popover_message_regions <- c("USA and Canada", "Latin America", "The mainland of South America", "Southern Africa", "Mid eastern Africa", "North western Africa", "Western Europe and Scandinavia", "Eastern Europe and Russia", "The oil-states and western Azia", "South Eastern Azia", "Mid Azia without Russia", "Australia, New Zealand and Papoea New-Guinea", "All the small islands and archipelago")

Confirmed_rate_per_million <- Confirmed_cases/Population*1000000

Death_rate_per_million <- Death_cases/Population*1000000

corona_continents_regions <- data.frame(Continent, Region, Population, Confirmed_cases, Death_cases, Confirmed_rate_per_million, Death_rate_per_million, popover_message_regions)


corona_western_countries <- data.frame(western_countries, western_countries_pop, western_countries_confirmed, western_countries_deaths, western_countries_confirmed_rate, western_countries_deaths_rate, news_states_western_countries)

# New dataset including the states and UK Italy and spain

states_uk_sp_it <- c("New York", "New Jersey", "California", "Illinois", "Massachusetts", "Texas", "Pennsylvania", "Florida", "Michigan", "Maryland", "Georgia", "Virginia", "Louisiana", "Connecticut", "North Carolina", "Ohio", "Indiana", "Arizona", "Tennessee", "Minnesota", "Colorado", "Alabama", "Washington", "Iowa", "Wisconsin", "South Carolina", "Missisipi", "Nebraska", "Rhode Island", "Missouri", "Utah", "Kentucky", "Arkansas", "Kansas", "Nevada", "Delaware", "New Mexico", "District of Columbia", "Oklahoma", "South Dakota", "Puerto Rico", "Oregon", "New Hampshire", "Idaho", "North Dakota", "Maine", "West Virginia", "Vermont", "Wyoming", "Hawaï", "Alaska", "Montana", "Guam", "US Virgin Islands", "Northern Mariana Islands", "American Samoa", "United Kingdom", "Spain", "Italy")
location <- c("USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA","USA", "USA", "USA", "USA", "USA","USA", "USA", "USA", "USA", "USA","USA", "USA", "USA", "USA", "USA","USA", "USA", "USA", "USA", "USA","USA", "USA", "USA", "USA", "USA","USA", "USA", "Washington D.C.", "USA", "USA","USA territory", "USA", "USA", "USA", "USA","USA", "USA", "USA", "USA", "USA","USA", "USA", "USA territory", "USA territory", "USA territory","USA territory", "Europe", "Europe", "Europe")
population_states_uk_sp_it <- c(19450000, 8882000, 39510000, 12670000, 6893000, 29000000, 12800000, 21480000, 9987000, 6046000, 10620000, 8536000, 4649000, 3565000, 10490000, 11690000, 6732000, 7279000, 6829000, 5640000, 5759000, 4903000, 7615000, 3155000, 5822000, 5149000, 2976000, 1934000, 1059000, 6137000, 3206000, 4468000, 3018000, 2913000, 3080000, 973764, 2097000, 705749, 3957000, 884659, 3194000, 4218000, 1360000, 1787000, 762062, 1344000, 1792000, 623989, 578759, 1416000, 731545, 1069000, 165768, 106977, 56882, 55465, 66650000, 46940000, 60360000)
conf_states_uk_sp_it <- c(384000, 167000, 151000, 134000, 105000, 87854, 77999, 75568, 65672, 60613, 57681, 53211, 46619, 44461, 44119, 40424, 39146, 35691, 30432, 29795, 28822, 25615, 25171, 23350, 22932, 18795, 18483, 16315, 15947, 15585, 13577, 11945, 11547, 11419, 10678, 10173, 9845, 9654, 7848, 5742, 5536, 5377, 5209, 3353, 3016, 2721, 2233, 1119, 1027, 728, 625, 573, 185, 72, 30, 0, 305000, 247000, 239000)
deaths_states_uk_sp_it <- c(24579, 12676, 5089, 6507, 7538, 1976, 6162, 2931, 5990, 2900, 2451, 1534, 3014, 4146, 1109, 2508, 2396, 1188, 475, 1305, 1595, 773, 1204, 644, 694, 600, 868, 212, 833, 872, 139, 493, 171, 245, 462, 414, 440, 506, 359, 74, 146, 173, 308, 87, 74, 100, 86, 55, 18, 17, 12, 18, 5, 6, 2, 0, 42647, 28324, 34657)

corona_states_uk_sp_it <- data.frame(states_uk_sp_it, location, population_states_uk_sp_it, conf_states_uk_sp_it, deaths_states_uk_sp_it)
```

On this page we going to look at the Corona data around the world. To do this, we are going to devide the world in regions. The regions are based on the continents and the northern, eastern, southern, western or combinations thereof. Some regions are regions with countries with a specific characteristic, such as islands in an specific ocean. In the table below we see all the regions. We see regions such as North America, where the name says a lot about the coutries in that region. But regions like Mid America, South Africa, etc. are vague. In the table is a column with extra information.

```{r create a table so the user can search the region and the abbreviation for each state, echo=FALSE, message=FALSE}
tab_regions <- corona_continents_regions %>% mutate(Extra_information = c("Canada and the USA","Main land of Latin America","Mainland of South America","African countries below the equator","Eastern African countries above the equator","Western African countries above the equator","Western Europe and Scandinavia","Eastern Europe and Russia","Oil states and western Azia","Countries located at the coast of the Indian Ocean and Indonesia","Mid Azia except Russia","Australia, New Zealand and Paopoea New-Guinea","Small island and archipelagos in the Pacific and the Atlantic"))%>% select(Region, Continent, Extra_information) 
kable(cbind(tab_regions)) %>% add_header_above(c("All the regions in the world" = 3)) %>% kable_styling("striped", "bordered") %>% scroll_box(width = "900px", height = "175px")
```

We have now the information the read the figures that we present on this page. 






```{r plot the locations of the continent regions in a scatter plot, echo=FALSE, message=FALSE}
corona_continents_regions %>% ggplot(aes(Population/10^6, Death_cases/10^3, label = Abb_region)) + geom_smooth(method = "gam") + geom_label_repel(aes(color = Reliability_test_capacity)) + geom_point() + ggtitle("Figure A; Amount of confirmed cases around the world and the 'average line'") + xlab("Population * 1.000.000") + ylab("Deaths * 1.000") + theme(legend.position = c(0.82, 0.79), legend.background = element_rect(fill = "lightblue", size = 0.5, linetype = "solid", color = "darkblue"))
```

```{r, echo=FALSE, message=FALSE}
corona_continents_regions %>% ggplot(aes(Population/10^6, Death_cases/10^3, label = Abb_region)) + geom_smooth(method = "glm") + geom_label_repel(aes(color = Reliability_test_capacity)) + geom_point() + ggtitle("Figure B;Amount of confirmed cases around the world and the 'average line'") + xlab("Population * 1.000.000, log 10 scale") + ylab("Deaths * 1.000") + scale_x_log10() + theme(legend.position = c(0.18, 0.79), legend.background = element_rect(fill = "lightblue", size = 0.5, linetype = "solid", color = "darkblue"))
```

```{r, echo=FALSE, message=FALSE}
corona_continents_regions %>% ggplot(aes(Population/10^6, Death_cases/10^3, label = Abb_region)) + geom_smooth(method = "gam") + geom_label_repel(aes(color = Reliability_test_capacity)) + geom_point(aes(color = Reliability_test_capacity)) + ggtitle("Figure C; Amount of death cases around the world and the 'average line'") + xlab("Population * 1.000.000") + ylab("Deaths * 1.000") + theme(legend.position = c(0.85, 0.79), legend.background = element_rect(fill = "lightblue", size = 0.5, linetype = "solid", color = "darkblue"))
```

```{r, echo=FALSE, message=FALSE}
corona_continents_regions %>% ggplot(aes(Population/10^6, Death_cases/10^3, label = Abb_region)) + geom_smooth(method = "gam") + geom_label_repel(aes(color = Reliability_test_capacity)) + geom_point(aes(color = Reliability_test_capacity)) + ggtitle("Figure D; Amount of death cases around the world and the 'average line'") + xlab("Population * 1.000.000, log 10 scale") + ylab("Deaths * 1.000") + scale_x_log10() + theme(legend.position = c(0.15, 0.79), legend.background = element_rect(fill = "lightblue", size = 0.5, linetype = "solid", color = "darkblue"))
```

```{r test width, echo=FALSE, message=FALSE}
corona_continents_regions %>% ggplot(aes(Population/10^6, Death_cases/10^3, label = Abb_region)) + geom_smooth(method = "gam") + geom_label_repel(aes(color = Reliability_test_capacity)) + geom_point(aes(color = Reliability_test_capacity)) + ggtitle("Figure D; Amount of death cases around the world and the 'average line'") + xlab("Population * 1.000.000, log 10 scale") + ylab("Deaths * 1.000") + scale_x_log10() + theme(legend.position = c(0.15, 0.79), legend.background = element_rect(fill = "lightblue", size = 0.5, linetype = "solid", color = "darkblue"))
```

```{r, echo=FALSE, message=FALSE}
corona_western_countries %>% ggplot(aes(western_countries_pop/10^6, western_countries_confirmed, label = western_countries)) + geom_label_repel(aes(color = news_states_western_countries)) + geom_point() + geom_smooth(method = "glm") + xlab("Population * 1.000.000") + ylab("Confirmed cases") + ggtitle("Figure E; Confirmed cases in the Western countries (Europe and N. America)") + theme(legend.position = c(0.23, 0.775), legend.background = element_rect(fill = "lightblue", size = 0.5, linetype = "solid", color = "darkblue")) 
```

```{r, echo=FALSE, message=FALSE}
corona_western_countries %>% ggplot(aes(western_countries_pop/10^6, western_countries_confirmed, label = western_countries)) + geom_label_repel(aes(color = news_states_western_countries)) + geom_point(aes(color = news_states_western_countries)) + geom_smooth(method = "gam") + scale_x_log10() + xlab("Population * 1.000.000") + ylab("Confirmed cases") + ggtitle("Figure F; Confirmed cases in the Western countries (Europe and N. America)") + theme(legend.position = c(0.23, 0.775), legend.background = element_rect(fill = "lightblue", size = 0.5, linetype = "solid", color = "darkblue")) 
```

```{r, echo=FALSE, message=FALSE}
corona_western_countries %>% ggplot(aes(western_countries_pop/10^6, western_countries_deaths/10^3, label = western_countries)) + geom_smooth(method = "glm") + geom_label_repel(aes(color = news_states_western_countries)) + geom_point(aes(color = news_states_western_countries)) + xlab("Population * 1.000.000") + ylab("death cases * 1.000") + ggtitle("Figure G; Death cases in the Western countries (Europe and N. America)") + theme(legend.position = c(0.23, 0.775), legend.background = element_rect(fill = "lightblue", size = 0.5, linetype = "solid", color = "darkblue")) 
```
```

```{r, echo=FALSE, message=FALSE}
corona_western_countries %>% ggplot(aes(western_countries_pop/10^6, western_countries_deaths/10^3, label = western_countries)) + geom_smooth(method = "glm") + geom_label_repel() + geom_point() + scale_x_log10() + xlab("Population * 1.000.000") + ylab("Death cases * 1.000") + ggtitle("Figure H; Deaths cases in the Western countries (Europe and N. America)") + theme(legend.position = "right", legend.background = element_rect(fill="lightblue", size=0.5, linetype = "solid", color = "darkblue")) + labs(color = "Regions the USA: ")
```

```{r,echo=FALSE, message=FALSE}
corona_states_uk_sp_it %>% ggplot(aes(population_states_uk_sp_it/10^6, conf_states_uk_sp_it/ 10^3, label = states_uk_sp_it)) + geom_smooth(method = "gam") + geom_label_repel(aes(color = location)) + geom_point(aes(color = location)) + scale_x_log10() +xlab("Population * 1.000.000") + ylab("Confirmed cases * 1.000") + ggtitle("Figure I; Confirmed cases of the states in the USA and Italy, Spain and the UK") + theme(legend.position = "right", legend.background = element_rect(fill="lightblue", size=0.5, linetype = "solid", color = "darkblue")) + labs(color = "Regions the USA: ")
```

```{r,echo=FALSE, message=FALSE}
corona_states_uk_sp_it %>% ggplot(aes(population_states_uk_sp_it/10^6, deaths_states_uk_sp_it/ 10^3, label = states_uk_sp_it)) + geom_smooth(method = "gam") + geom_label_repel(aes(color = location)) + geom_point(aes(color = location)) + scale_x_log10() +xlab("Population * 1.000.000") + ylab("Death cases * 1.000") + ggtitle("Figure J; Death cases of the states in the USA and Italy, Spain and the UK") + theme(legend.position = "right", legend.background = element_rect(fill="lightblue", size=0.5, linetype = "solid", color = "darkblue")) + labs(color = "Regions the USA: ")
```